\documentclass[11pt,a4paper,sans]{moderncv}

\moderncvtheme[blue]{classic}

\usepackage[utf8]{inputenc}

\usepackage[scale=0.9, top=1cm, bottom=1cm, left=1.5cm, right=1.5cm]{geometry}

% personal data

% personal data
\firstname{Arron}
\familyname{Norwell}

\extrainfo{Medford, MA \\ anorwell.com \\ github.com/ANorwell}
\phone{857-266-4119}
\email{anorwell@gmail.com}


\newcommand{\up}[1]{\ensuremath{^\textrm{\scriptsize#1}}}

 % the ConTeXt symbol
\def\ConTeXt{%
  C%
  \kern-.0333emo%
  \kern-.0333emn%
  \kern-.0667em\TeX%
  \kern-.0333emt}
\definecolor{web}{rgb}{0.2,0.2,0.2}
%\definecolor{web}{rgb}{0.5,0.5,0.5}
%----------------------------------------------------------------------------------
%            content
%----------------------------------------------------------------------------------
\begin{document}
\pagestyle{empty}
\maketitle

\section{\textbf{Summary}}

   \cvline{}{A results-oriented engineer with expertise in building scalable distributed systems and agentic AI development. Experience building products from zero to one supporting millions of users, with deep knowledge of infrastructure platforms, performance, reliability, and leading teams in fast-moving environments.}


\section{\textbf{Skills}}


      \cvlistdoubleitem{Distributed Systems}
                       {Scalability and Performance Optimization}
      \cvlistdoubleitem{REST APIs and Platform Architecture}
                       {Agentic AI Development Tooling}
      \cvlistdoubleitem{Cloud (AWS, Google Cloud, Azure)}
                       {Software Architecture and Design}
      \cvlistdoubleitem{Relational DBs (Postgres, MySQL)}
                       {NoSQL (DynamoDB, Elasticsearch, Redis)}
      \cvlistdoubleitem{DevOps (CI/CD, CDK, Containers)}
                       {OpenAPI, Protobuf}


%\subsection{\textbf{Languages}}

  \cvline{Languages:}{Java, Python, Rust, Scala, Ruby, Go, Typescript, Javascript}


\section{\textbf{Experience}}

\cventry{Oct 2020 - Present}{\textbf{Senior Software Engineer}}{Amazon Web Services (EFS)}{}{Boston, MA}
{ \begin{itemize} \itemsep -2pt
  \item Led agentic AI and GenAI coding adoption across EFS organization (50+ engineers), including tooling development, training, and coding agent supervision tools.
  \item Algorithm designer and correctness lead for large-scale data synchronization platform, ensuring consistency guarantees across distributed storage systems.
  \item Designed and created operational and bugfixing agents used by the EFS organization to automate common workflows, reducing manual toil and improving incident response times.
  \item Designed and built distributed filesystem cross-region replication platform using Java, Python, and AWS CDK.
  \item Built end-to-end simulation system for fault-tolerant distributed systems, adopted by multiple teams to improve developer throughput and increase system resilience.
 \end{itemize} }

\cventry{June 2017 - Oct 2020}{\textbf{Principal Software Engineer}}{Datto}{}{Boston, MA}
{ \begin{itemize} \itemsep -2pt
  \item Initial engineer and technical lead on greenfield SaaS platform redesign using Scala, Elasticsearch, and ZFS. Platform supports millions of users and dozens of petabytes of data.
  \item Built reusable monitoring platform handling hundreds of millions of events daily; prototyped features including backup visualization and Azure Exchange restore.
  \item Provided architectural guidance and mentoring to three scrum teams; collaborated on product roadmap and technical direction.
 \end{itemize} }

  \cventry{Nov 2013 - June 2017}{\textbf{Senior Software Engineer}}{Datto}{}{Boston, MA}
{ \begin{itemize} \itemsep -2pt
  \item Built distributed backup system supporting 1M+ daily users using Ruby on Rails, Redis, PostgreSQL, Cassandra, and S3.
  \item Led 7-developer team delivering Office 365 Backup/Restore solution on schedule.
  \item Created open-source Cassandra client and API framework handling tens of millions of daily requests.
\end{itemize} }

  \cventry{Apr 2012 - Nov 2013}{\textbf{Software Developer / Team Lead}}{mDialog (acquired by Google)}{}{Toronto, ON}
{ \begin{itemize} \itemsep -2pt
  \item Fourth engineer at Series A video streaming startup acquired by Google; built distributed platform from zero to one in Scala/Java/C scaling to 250K concurrent streams.
\end{itemize} }


\section{\textbf{Education}}
\cvline{}{\textbf{M.Sc. Computer Science}, University of Toronto (2012) • \textbf{B.Sc. Mathematics/CS}, UBC (2009)}

\section{\textbf{Selected Projects}}
\cvline{}{Open source: Claippy (Rust GenAI CLI coding tool), CassSchema, Pyper • Personal: anorwell.com, SNPReporter (Rust genetic analysis)}
%\section{\textbf{Publications}}



\end{document}
